---
title: "Brook Trout Morphometrics"
author: "Brian Cheng"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(lme4)
library(lmerTest)
library(emmeans)
```

## R Markdown

Morphometrics refers to all aspects of brook trout morphology that were measured.   
* Weight  
* Length 
* Sex (for fish that were sampled)   

It also refers to calculated metrics, such as:   
* SGR (specific growth rate)  
* Condition factor (K)  
* TGC (thermal growth coefficient)   

With long format data

```{r}
morph_long<-read.csv(here('data/BT_Morphometrics_LongForm_Merged_05032023.csv'), stringsAsFactors = T)
str(morph_long)

morph_long <- morph_long %>%
  mutate (temp = factor(substr(TANK_Real, 1, 2)))%>%
  mutate (TANK_Real = factor(TANK_Real)) %>%
  mutate (rdate = as.POSIXct(x=TIME, format = "%Y-%m-%d")) %>%
  mutate (K = WEIGHT*100*(LENGTH^-3)) %>%
  rename ("tank" = "TANK_Real") %>%
  rename ("time_step" = "condition3")
  
str(morph_long)
#unique(morph_long$TIME)
#K = Mass*(Length^-3)
morph_long_inital<-morph_long %>% filter (time_step =="T1")
```
Data Tidying
```{r}
sum(is.na(morph_long$WEIGHT)) #676 Weight NAs
sum(is.na(morph_long$LENGTH)) #678 Length NAs
morph_long2<-morph_long %>%
  drop_na(WEIGHT) %>%
  drop_na(LENGTH)
summary(morph_long2) #now has 2100 obs
freq_tab<-morph_long2 %>%
  count(tank, time_step) %>%
  group_by(tank)
freq_tab
ggplot(data=freq_tab, aes(x=time_step,y=n, group = tank, color = tank))+geom_line()
```

Calculate
```{r}
#create summary df for weight mean and sem
bt_means2<-tapply(morph_long2$WEIGHT,list(morph_long2$temp,morph_long2$time_step),mean)
bt_sd2   <-tapply(morph_long2$WEIGHT,list(morph_long2$temp,morph_long2$time_step),sd)
bt_count2<-tapply(morph_long2$WEIGHT,list(morph_long2$temp,morph_long2$time_step),length)
bt_sem2  <-bt_means2/sqrt(bt_count2)

weight_means<-data.frame(bt_means2)
weight_means$C_temp<-row.names(weight_means)
weight_means2<-weight_means %>%
  pivot_longer(cols = starts_with("T"),
               names_to = "time_step",
               names_prefix = "T",
               values_to = "mean_weight")

weight_se<-data.frame(bt_sem2)
weight_se$C_temp<-row.names(weight_se)
weight_se2<-weight_se %>%
  pivot_longer(cols = starts_with("T"),
               names_to = "time_step",
               names_prefix = "T",
               values_to = "se_weight")
#now merge the dataframes
weight_mean_se<- left_join(weight_means2, weight_se2, by = c("time_step", "C_temp"))
```


EDA

```{r}
morph_long %>%
  count(TANK_Real, condition3) %>%
  group_by(TANK_Real)
```

Are there differences in initial size?

```{r}
str(morph_long2)
ggplot(data = morph_long_inital, aes(x=tank, y=WEIGHT))+geom_boxplot()
ggplot(data = morph_long_inital, aes(x=tank, y=LENGTH))+geom_boxplot()
init_w<-glm(data=morph_long_inital, formula = WEIGHT ~ tank, family = gaussian())
init_l<-glm(data=morph_long_inital, formula = LENGTH ~ tank, family = gaussian())
summary(init_w)
summary(init_l)
```
No evidence for differences across tank treatments with respect to initial WEIGHT or LENGTH. 

How about differences in length and weight over time?

```{r}
A_col <- "#9933FF"
B_col <- "#FF6666"
str(weight_mean_se)
plot1<-ggplot(weight_mean_se, aes(x=time_step, y=mean_weight, color = C_temp))+geom_point()+
  geom_errorbar(data=weight_mean_se, aes(ymin=mean_weight-se_weight, ymax = mean_weight+se_weight),
                width=0, size = 1)+
  geom_point(size = 3, fill = "white")+geom_line()+
  labs(y=expression(paste("Weight (mean grams \U00B1SEM)")), x="Time Step")+
  theme_bw()+theme(legend.title=element_text(size=16),legend.text=element_text(size=14),
        axis.text.y=element_text(size=16),axis.title.y=element_text(size=18, vjust=1.2),
        axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_fill_manual(values  = c(A_col, B_col)) +
  scale_color_manual(values = c(A_col, B_col))
plot1
ppi=300
png('figures/mass_time_series.png', width=9*ppi, height=6*ppi, res=ppi)
plot1
dev.off()
```

Definitely differences across temps. Slight tank effects

```{r}
length01<-lmer(LENGTH ~ temp * time_step + (1|TAGNUMBER), data = morph_long2)
length02<-lmer(LENGTH ~ temp * time_step + (1|TAGNUMBER) + (1|tank), data = morph_long2)

summary(length01)
summary(length02)

anova(length01, ddf = "Kenward-Roger")
anova(length02, ddf = "Kenward-Roger")

emm1 = emmeans (length01, ~ temp | time_step)
contrast(emm1, contrast = TRUE)
pairs(emm1)
pairs(emm1, by = "temp")
plot(emm1)
```
Most sensible model for length is fixed effects of temperature, time steps, and their interaction. It is possible to model with a crossed random effect of tank (since there are 4) but this would only really make sense if random tanks were nested within temperature, which overfits the data. So I think random effects of repeated measures on individuals makes the most sense. 

```{r}
morph_long2$resid<-resid(length01)
str(morph_long2)
ggplot(morph_long2, aes(x=tank, y = resid))+geom_boxplot()+geom_point()
ggplot(morph_long2, aes(x=time_step, y = resid))+geom_boxplot()+geom_point()
ggplot(morph_long2, aes(x=time_step, y = resid))+geom_boxplot()+geom_point()+facet_grid(.~tank)

```
Residuals for length model looks good. Now moving on to weight. 

```{r}
weight01<-lmer(WEIGHT ~ temp * time_step + (1|TAGNUMBER), data = morph_long2)
weight02<-lmer(WEIGHT ~ temp * time_step + (1|TAGNUMBER) + (1|tank), data = morph_long2)

summary(weight01)
summary(weight02)

anova(length01, ddf = "Kenward-Roger")
anova(length02, ddf = "Kenward-Roger")

emm2 = emmeans (weight01, ~ temp | time_step)
contrast(emm2, contrast = TRUE)
pairs(emm2)
pairs(emm2, by = "temp")
plot(emm2)
```

