---
title: "Brook Trout Morphometrics"
author: "Brian Cheng"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
```

## R Markdown

Morphometrics refers to all aspects of brook trout morphology that were measured.   
* Weight  
* Length 
* Sex (for fish that were sampled)   

It also refers to calculated metrics, such as:   
* SGR (specific growth rate)  
* Condition factor (K)  
* TGC (thermal growth coefficient)   

With long format data

```{r}
morph_long<-read.csv(here('data/BT_Morphometrics_LongForm_Merged_04042023.csv'), stringsAsFactors = T)
str(morph_long)

morph_long <- morph_long %>%
  mutate (TANK_Real = factor(TANK_Real)) %>%
  mutate (rdate = as.POSIXct(x=TIME, format = "%Y-%m-%d")) %>%
  mutate (K = WEIGHT*100*(LENGTH^-3)) %>%
  rename ("tank" = "TANK_Real") %>%
  rename ("time_step" = "condition3")
str(morph_long)
#unique(morph_long$TIME)
#K = Mass*(Length^-3)
morph_long_inital<-morph_long %>% filter (time_step =="T1")
```
Data Tidying
```{r}
sum(is.na(morph_long$WEIGHT)) #676 Weight NAs
sum(is.na(morph_long$LENGTH)) #678 Length NAs
morph_long2<-morph_long %>%
  drop_na(WEIGHT) %>%
  drop_na(LENGTH)
summary(morph_long2) #now has 2100 obs
freq_tab<-morph_long2 %>%
  count(tank, time_step) %>%
  group_by(tank)
ggplot(data=freq_tab, aes(x=time_step,y=n, group = tank, color = tank))+geom_line()
```


EDA

```{r}
ggplot(data = morph_long, aes(x=rdate, y=WEIGHT, color = TANK_Real))+geom_point()


morph_long %>%
  count(TANK_Real, condition3) %>%
  group_by(TANK_Real)
```

Are there differences in initial size?

```{r}
ggplot(data = morph_long_inital, aes(x=TANK_Real, y=WEIGHT))+geom_boxplot()
ggplot(data = morph_long_inital, aes(x=TANK_Real, y=LENGTH))+geom_boxplot()
init_w<-glm(data=morph_long_inital, formula = WEIGHT ~ TANK_Real, family = gaussian())
init_l<-glm(data=morph_long_inital, formula = LENGTH ~ TANK_Real, family = gaussian())
summary(init_w)
summary(init_l)
```
No evidence for differences across tank treatments with respect to initial WEIGHT or LENGTH. 
